% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Wenshuo Xu}

\basicInfo{
  \email{wenshuo.xu@mail.utoronto.ca} \textperiodcentered\ 
  \phone{365-888-3946} \textperiodcentered\ 
  \linkedin[Wenshuo Xu]{linkedin.com/in/wenshuo-xu/} \textperiodcentered\ 
  \github[brianxxx1]{https://github.com/brianxxx1/}}

\section{\faChild\ Summary}
\textit Passionate and results-driven Software Engineer with extensive expertise in designing, implementing, and maintaining SAAS applications on AWS. Adept at leveraging cloud services to deliver scalable and secure solutions. Proven ability to collaborate with cross-functional teams to deliver high-quality software products.

\section{\faKey\ Highlights}
\begin{itemize}[parsep=0.5ex]
  \item Proficient in Python and Java with a strong understanding of Object-Oriented Programming.
  \item Familiar with popular design patterns.
  \item Experience with Java/Python web development frameworks (SpringBoot, FastAPI, Flask).
  \item Proficient in SQL/NoSQL databases, including schema design (MySQL, DynamoDB, Redis).
  \item Experienced in CI/CD pipelines.
  \item Expereienced in building SAAS applications with AWS.
\end{itemize}

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{University of Toronto}, Toronto, Canada}{2022 -- Present}
\textit{Master of Engineering} in Computer Engineering, expected May 2025
\datedsubsection{\textbf{McMaster University}, Hamilton, Canada}{2017 -- 2022}
\textit{B.S.} in Mechatronics Engineering

\section{\faUsers\ Experience}
\datedsubsection{\textbf{McMaster University} Hamilton, Canada}{Jan 2022 -- June 2022}
\role{Research Assistant}{Supervising Professors: Dr.Richard Paige and Dr.Vera Pantelic}
Deisgned and implemented a web-based traffic monitoring tool for a fare collection system for an industrial partner in US
\begin{itemize}
  \item Received live events from Kafka, calculated metrics and stored data in database.
  \item Tech Stack: NodeJS, Kafka, Docker, PostgreSQL, React.
  \item Mainly involved in backend development and database design.
\end{itemize}

\datedsubsection{\textbf{Evertz Microsystems Inc} Burlington, Canada}{July 2022 -- Present}
\role{SDE} {Designed and developed a multi-tenant, scalable, and resilient SAAS application.}
\begin{itemize}
  \item Worked on infrastructure services (authorizer, websocket management, tenant management, etc.)
  \item Designed and implemented a service that integrates existing hardware products into the SAAS application from scratch.
  \item Conducted code reviews, mentored interns, and provided technical leadership.
\end{itemize}

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Programming Languages: Python > Java > C > Node
  \item Database: MySQL, DB2, PostgreSQL, DynamoDB, Redis.
  \item Web Frameworks: SpringBoot, FastAPI, Flask.
  \item Cloud Services: AWS (Lambda, EC2, IAM, VPC, S3, StepFunctions, SNS, SQS, EventBridge).
  \item CI/CD: AWS CodePipelines, GitHub Actions, Jenkins, Maven.
  \item Testing: PyTest, JUnit.
  \item Version Control: Git.
  \item Infrastructure as Code (IaC): AWS CDK, AWS CloudFormation.
  \item Monitoring and Logging: AWS CloudWatch, Honeycomb.
  \item Others: Tomcat, HTML+CSS+JavaScript, JSON, JSP, Nginx, RabbitMQ.
\end{itemize}

\section{\faHeartO\ Honors and Awards}
\datedline{Dean’s Honor List for 4 consecutive years}{2018 -- 2022}
\datedline{Provost Honour Roll (Awarded to students with full GPA for the whole school year)}{2022}

\section{\faFolderO\ Projects}
\datedsubsection{Database and Data Analysis System for PLC}{June 2020 -- May 2021}
Deisgned and implemented a web-based traffic monitoring tool for a fare collection system for an industrial partner in US
\begin{itemize}
  \item System includes login/logout, data persistance/retrieval, remote plant monitoring and operation, data export, graphing, and analysis.
  \item Tech Stack: SpringBoot, Mybatis, Tomcat, MySQL, jQuery.
  \item Designed, implemented, tested, and deployed independently.
\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
